On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-26 response.tex

\begin{document}

\title{Response to the Reviews}
\author{Shiyu Ji}
\maketitle

\begin{questions}
\section{Reviewer 1}
\question Several key issues are not presented clearly, making the paper hard to be followed. For instance, the paper discussed the n-truthful property of the proposed mechanism, during which the authors assumed that the proposed mechanism is strategyproof. So, it is better to give a lemma or a theorem to explicitly prove that the proposed mechanism is strategyproof. Actually, only Lemma 3 in this paper is related to this issue. Nevertheless, this Lemma still has not shown the strategyproof property explicitly. This makes the readers hard to follow this paper, especially for the readers who do not know this area very well. The paper requires the reader to be familiar with the theory of auctions. It is better to spend more time giving some background on auctions. 
\begin{solution}
I have made Lemma 3 more clear. Now it clearly states that for the given $n_i$ profile, the discrete crowdsensing game achieves strategyproof equilibrium. I also gave some texts before Lemma 3: before we introduce our main results, we need Lemma 3, which gives the strategyproof equilibrium for the discrete crowdsensing game. Hope by doing this the readers can better follow the logic flow. 
\end{solution}

\question The model in this paper has some limitations. The authors did not consider some important issues in the platform, which are generally concerned in other papers, such as the number of tasks to be finished and the budget constraint of the platform to finish these tasks. When these issues are taken into consideration, the problem might become more difficult. Despite this, it is better to give an explanation or discussion on this, to make the proposed mechanism practical. 
\begin{solution}
I have revised the main algorithm to consider these factors: the number of tasks to finish and the budget constraint. This is done by adding the number of sensing tasks $R$ and the budget constraint $n\cdot P_m < B$, where $n$ is the entire user population, $P_m$ is the maximum payment to any user and $B$ is the upper bound of the budget. I have also reflected these changes and evaluated their performance in the experimental section. Hope by doing this our mechanism can have more practical value.
\end{solution}

\question In this paper, the authors assume that the range of each user’s cost unit is known to the platform and each user has a maximum payment. The proposed mechanism totally relies on the parameters in the assumption. However, the paper did not mention how to get the parameters in a real crowdsensing system.
\begin{solution}
The range of each user cost unit can be inferred from historical records. This point has been verified by Koutsopoulos's work. I have also clarified how to choose the maximum payment $P_m$. It can be related to the budge $B$ satisfying $n\cdot P_m < B$. From the experiments, usually each game can only assume less than 10\% of the budget. Thus the game is budget-feasible. 
\end{solution}

@@

\question Some important related literatures are missing.

\section{Reviewer 2}
\question In Section VII, the simulations demonstrate that the authors’ crowdsensing incentive mechanism can achieve group strategyproof and n-truthful equilibrium simultaneously. However, if we do not consider the collusion attack problem, how are about the performance of the proposed crowdsensing incentive mechanism compared to other existing ones? The authors did not discuss it.  
\begin{solution}
Previously the experiment design is not good, since to show the security properties such as achieving group strategyproofness, one has to do it in theory rigorously, rather than simulations. Now I decide to rebuild the experiments and compare the performance of our mechanism to other works such as Koutsopoulos's.
\end{solution}

### 2015-12-26 response.tex

\renewcommand{\solutiontitle}{\noindent\textbf{Response:}\par\noindent}

\begin{document}

\title{Response to the Reviews}
\author{Shiyu Ji}
\maketitle

\begin{questions}
\section{Reviewer 1}
\question Several key issues are not presented clearly, making the paper hard to be followed. For instance, the paper discussed the n-truthful property of the proposed mechanism, during which the authors assumed that the proposed mechanism is strategyproof. So, it is better to give a lemma or a theorem to explicitly prove that the proposed mechanism is strategyproof. Actually, only Lemma 3 in this paper is related to this issue. Nevertheless, this Lemma still has not shown the strategyproof property explicitly. This makes the readers hard to follow this paper, especially for the readers who do not know this area very well. The paper requires the reader to be familiar with the theory of auctions. It is better to spend more time giving some background on auctions. 
\begin{solution}
I have made Lemma 3 more clear. Now it clearly states that for the given $n_i$ profile, the discrete crowdsensing game achieves strategyproof equilibrium. I also gave some texts before Lemma 3: before we introduce our main results, we need Lemma 3, which gives the strategyproof equilibrium for the discrete crowdsensing game. Hope by doing this the readers can better follow the logic flow.

Our mechanism is not a typical auction, since there is no selection phase. In our mechanism every user can be a winner, if finishing the task will not cause any negative utility to the user. We have not used any auction theory in our analysis. Thus I think it is enough to give details about the typical crowdsensing model in many existing papers in Section III.A. The readers can well understand our mechanism even without any background of auction theory. On the other hand, it is a good idea to give some citations to auction-based mechanisms in the related works section. But I want to be brief since they are not quite relevant to this paper.
\end{solution}

### 2015-12-26 techreport.tex
Address Item 1, Review 1.

\section{Related Works}
\label{sec:rw}
Incentive mechanism design in crowdsensing applications has attracted a lot of attention in research \cite{ganti2011mobile, singer2013pricing, vukovic2010ubiquitous, yang2012crowdsourcing, zhao2012evaluation, koutsopoulos2013optimal, zhang2012reputation, singla2013truthful, jaimes2012location, singla2013incentives}. Among them the question how to make the participating users strategize truthfully has a lot of interests \cite{singer2013pricing, vukovic2010ubiquitous}. For example, Yang et al. \cite{yang2012crowdsourcing} proposed a truthful user-centric incentive mechanism for mobile phone crowdsensing. They used the truthful auction rule (Theorem 2.1 in \cite{singer2010budget}) to implement the computationally efficient mechanism in which each user had no incentive by lying about its cost. But the authors did not consider the scenario that the platform budget could be limited. To make the mechanism budget feasible, Singla et al. \cite{singla2013truthful} proposed another truthful incentive mechanism by making a few assumptions on each user's cost distribution. Similarly, Koutsopoulos \cite{koutsopoulos2013optimal} gave the closed form of truthful incentive payments for some continuous crowdsensing games by assuming each user's cost value is bounded within an interval. On the other hand, one may consider many other factors when designing incentive mechanisms for crowdsensing applications. Such factors include reputation mechanisms \cite{zhang2012reputation}, users' locations \cite{jaimes2012location}, privacy concerns \cite{singla2013incentives}, etc. Unfortunately, many of them could not achieve truthful mechanisms \cite{zhang2012reputation, jaimes2012location}.

>>>>

\section{Related Works}
\label{sec:rw}
Incentive mechanism design in crowdsensing applications has attracted a lot of attention in research \cite{ganti2011mobile, singer2013pricing, vukovic2010ubiquitous, yang2012crowdsourcing, zhao2012evaluation, koutsopoulos2013optimal, zhang2012reputation, singla2013truthful, jaimes2012location, singla2013incentives, dipalantino2009crowdsourcing, feng2014trac, liu2011crowdsourcing}. Among them the question how to make the participating users strategize truthfully has a lot of interests \cite{singer2013pricing, vukovic2010ubiquitous}. For example, Yang et al. \cite{yang2012crowdsourcing} proposed a truthful user-centric incentive mechanism for mobile phone crowdsensing. They used the truthful auction rule (Theorem 2.1 in \cite{singer2010budget}) to implement the computationally efficient mechanism in which each user had no incentive by lying about its cost. But the authors did not consider the scenario that the platform budget could be limited. To make the mechanism budget feasible, Singla et al. \cite{singla2013truthful} proposed another truthful incentive mechanism by making a few assumptions on each user's cost distribution. Similarly, Koutsopoulos \cite{koutsopoulos2013optimal} gave the closed form of truthful incentive payments for some continuous crowdsensing games by assuming each user's cost value is bounded within an interval. {\color{blue}\cite{dipalantino2009crowdsourcing,feng2014trac,liu2011crowdsourcing} gave truthful mechanisms based on auction theory.} On the other hand, one may consider many other factors when designing incentive mechanisms for crowdsensing applications. Such factors include reputation mechanisms \cite{zhang2012reputation}, users' locations \cite{feng2014trac,jaimes2012location}, privacy concerns \cite{singla2013incentives}, etc. Unfortunately, many of them could not achieve truthful mechanisms \cite{zhang2012reputation, jaimes2012location}.
